FinalManuscript_DISCS_UG

### 2019-01-21 pcsc-paper/parts/01_introduction.tex
Added experiments
We have a mini-thesis na
Done!
conclusion and reccomendations
Minor fixes
Comments to intro/conclusion
Attempt to take into account sir's comments
3rd draft
apply 2nd round of comments

\section{Introduction}
Research in digital privacy has involved the use of homomorphic cryptosystems, cryptosystems which allow for operations to be performed on encrypted data without leaking information about the operands.
Previous research has highlighted the use of the Paillier cryptosystem, a partially homomorphic cryptosystem which allows two basic operations to be performed on encrypted integers: two encrypted integers can be added to obtain an encryption of their sum, and an encrypted integer can be multiplied to an unencrypted plaintext integer to obtain an encryption of their product.

Applications of the Paillier cryptosystem have included such as use in linear digital image transformations~\cite{ziad_cryptoimg:_2016}, and linear algebra applications~\cite{hutchison_privacy-preserving_2009}. However, many extensions to the Paillier cryptosystem have also been published, allowing floating-point arithmetic. In this paper, we will summarize these extensions and concern ourselves with the approximation of the transcendental functions using the Paillier cryptosystem given input constraints shown in Table~\ref{tab:inputconstraints}. By demonstrating how the Paillier cryptosystem can be applied to approximate common non-linear functions, we hope to extend its usability as a tool for privacy-preserving computation.
\begin{table}
	\caption{Summary of functions [WIP]}
	\label{tab:inputconstraints}
	\begin{tabular}{ccl}
		\toprule
		Functions & Input constraints\\
		\midrule
		$e^x$ & $x\in[0,255]$\\
		$\log(1+x)$ & $x\in[0,255]$\\
		$\sin x$ & $x\in[-2\pi,2\pi]$ \\
		$\arctan x$ & $x\in[-255,255]$\\
		\bottomrule
\end{tabular}
\end{table}

>>>>

\section{Introduction}
Research in digital privacy has involved the use of homomorphic cryptosystems that allow for operations to be performed on encrypted data without leaking information about the operands.
Previous research has highlighted the use of the Paillier cryptosystem, a partially homomorphic cryptosystem which allows two basic operations to be performed on encrypted integers: two encrypted integers can be added to obtain an encryption of their sum, and an encrypted integer can be multiplied to an unencrypted plaintext integer to obtain an encryption of their product.

Applications of the Paillier cryptosystem have included such as use in linear digital image transformations~\cite{ziad_cryptoimg:_2016}, and linear algebra applications~\cite{hutchison_privacy-preserving_2009}. However, many extensions to the Paillier cryptosystem have also been published, allowing floating-point arithmetic. In this paper, we will summarize these extensions and concern ourselves with the approximation of the transcendental functions using the Paillier cryptosystem given input constraints shown in Table~\ref{tab:inputconstraints}. By demonstrating how the Paillier cryptosystem can be applied to approximate common non-linear functions, we hope to extend its usability as a tool for privacy-preserving computation.

The functions in Table~\ref{tab:inputconstraints} were chosen since current approximations of these functions which can easily be computed through privacy-preserving artihmetic are limited in their range of accuracy.
\begin{table}
	\caption{Summary of functions}
	\label{tab:inputconstraints}
	\begin{tabular}{ccl}
		\toprule
		Functions & Input constraints\\
		\midrule
		$\log\left(1+x\right)$ & $x\in[0,255]$\\
		$\arctan x$ & $x\in[-1,1]$\\
	    \bottomrule
    \end{tabular}
\end{table}

### 2019-01-21 pcsc-paper/parts/06_conclusionreccomendations.tex
Additional recommendation
Additional recommendation
3rd draft
apply 2nd round of comments

\section{Conclusion}
We have shown new closed-form approximations to the logarithm and inverse tangent functions and showed how they can be implemented together with the Paillier cryptosystem to allow for privacy-preserving function calculation. We have compared our approach to other closed-form approximations which require a similar number of secure arithmetic operations to evaluate, and have shown our new approximation procedures can generally yield more accurate results over larger ranges of inputs.

@@

\section{Recommendations}
Further research can be done regarding implementation of other transcendental functions, either by using known infinite series, or by using identities with the quadrature-based approximations we have presented in this paper. Furthermore, testing with other types of homomorphic cryptosystems can be done, to potentially reduce noise encountered in secure floating-point operations.

>>>>

\section{Conclusion}
We have shown new closed-form approximations to the logarithm and inverse tangent functions and showed how they can be implemented together with the Paillier cryptosystem to allow for privacy-preserving function calculation. We have compared our approach to other closed-form approximations which require a similar number of secure arithmetic operations to evaluate, and have shown our new approximation procedures can generally yield more accurate results over larger ranges of inputs. In particular, the error in the original approximation for $\log{\left(1+x\right)}$ increases quickly over inputs greater than 52, while the error in our new logarithm approximation increases slower, allowing our new approximation to be used for applications where accuracy is desired over a larger range of inputs.
Futhermore, as seen in Table~\ref{tab:arctan_approximation}, our new inverse tangent approximation is an order of magnitude better than the sum of the first five terms of the series by Euler in Equation~\ref{eq:arctan_euler}, despite requiring a similar number of floating-point operations.

@@

\section{Recommendations}
Further research can be done regarding implementation of other transcendental functions, either by using known infinite series, or by using identities with the quadrature-based approximations we have presented in this paper. Different methods for numerical integration can also be explored and applied for use in deriving formulas for privacy-preserving computation. Furthermore, testing with other types of homomorphic cryptosystems can be done, to potentially reduce noise encountered in secure floating-point operations.
